### 2017-05-11 uw-ethesis-frontpgs.tex
Add files via upload

>>>>

		Symbol & Unit & Property \\
		\midrule
		$C$ & \si{\joule} & heat capacity \\
		FOV & \si{\deg} & sensor field of view \\
		\textit{H} & \si{\meter} & building width \\
		$Q*$ & \si{\watt\per\square\meter} & net radiation flux density \\
		$\Delta Q_A$ & \si{\watt\per\square\meter} & net advective heat flux density \\
		$\Delta Q_G$ & \si{\watt\per\square\meter} & net heat storage flux density \\
		$Q_E$ & \si{\watt\per\square\meter} & latent heat flux density \\
		$Q_F$ & \si{\watt\per\square\meter} & anthropogenic heat flux density \\
		$Q_H$ & \si{\watt\per\square\meter} & sensible heat flux density \\
		$t$ & \si{\minute} & time \\
		T\textsubscript{air} & \si{\kelvin} & air temperature \\
		T\textsubscript{comp} & \si{\kelvin} & complete urban surface temperature\\
		T\textsubscript{hem} & \si{\kelvin} & urban surface temperature viewed from a hemispherical remote sensor\\
		T\textsubscript{plan} & \si{\kelvin} & urban surface temperature viewed from a sensor in the nadir\\
		T\textsubscript{road} & \si{\kelvin} &road surface temperature\\
		T\textsubscript{roof} & \si{\kelvin} & roof surface temperature \\
		T\textsubscript{surf} & \si{\kelvin} & surface temperature \\
		T\textsubscript{wall} & \si{\kelvin} & wall surface temperature\\

		aUHI & \si{\kelvin} & air temperature urban heat island effect \\
		clUHI & \si{\kelvin} & canopy layer air temperature urban heat island effect \\
		sUHI & \si{\kelvin} & surface temperature urban heat island effect \\
		$V_B$ & - & effects from background climate on observation of a given meteorological variable \\
		$V_H$ & - & effects from the urban environment on observation of a given meteorological variable \\
		$V_L$ & - & effects from local topography on observation of a given meteorological variable \\
		$V_M$ & - & observed meteorological variable \\
		$V_{M, U} $ & - & observed meteorological variable (urban) \\
		$V_{M  R}$ & - & observed meteorological variable (rural) \\
		$z$ & \si{\meter} & layer thickness (air, surface, or subsurface)\\
		\bottomrule
	\end{tabular} 
\end{table}
